### 2015-05-26 poisson_errker.tex
Updating poisson section

Using the analytic solution~\eqref{eq:analytic} and the sine series
representation of the Green's function~\eqref{eq:green}, it is easy to show that
the solution is given by
\begin{equation}
  \st{V}[\vect{m}] = -
  \frac{\st{f}[\vect{m}]}{\pi^2 \norm{\vect{m}}^2},
\label{eq:fourierSolution}
\end{equation}
where $\vect{m} \in \ints^s_+$ and $\st{f}[\cdot]$ represents the Fourier
sine series coefficients of the odd extension of $f$. To facilitate subsequent
discussions, let us introduce the solution operator
$\stpairs{\invlaplacian}{\frac{1}{-\pi^2 \norm{\vect{m}}^2}}$  ($\vect{m} \in
\ints^s_+$), where the symbol $\stpairs{}{}$ represents how the Fourier sine
series coefficients are affected by the operator.
%\begin{equation}
%V(\vect{x}) = \invlaplacian\Bigl( f(\vect{x}) +
%\sum_{i=1}^s D^0_i g^0_i(\vect{x}) + D^1_i g^1_i(\vect{x}) \bigr), 
%\label{eq:operatorAnalytic}
%\end{equation}
The self-adjoint operator $\invlaplacian$ is the inverse of the Laplace
operator. Self-adjointness can be easily verified with
the aid of Parseval's relation, which states that
$
  \innerproduct{a}{b} = \sum_{\vect{m} \in \ints^s_+} \st{a}[\vect{m}]
  \st{b}[\vect{m}] 
$
for any $\cube^s$-periodic functions $a$ and $b$ that are in
$L_2(\cube^s)$ and odd.

@@

We wish to use the samples of $f$ to seek an approximation $\appf{V}$ of the
function $V$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
$V$ is a periodic function, we follow the recipe of Jacob \textit{et
al.}~\cite{jacob02} and seek an approximation that lies in a space generated by
a periodic reconstruction function. Specifically, we are interested in the case
where $\appf{V}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} :=
\mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and
translated versions of a periodic function $\varphi_p$. Our sought-after
approximation is given by
\begin{equation}
  \appf{V}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{T}_h} c[\vect{x}_j] 
\varphi_p\bigl(\frac{\vect{x} - \vect{x}_j}{h}\bigr),
\label{eq:ansatz}
\end{equation}
where $c[\vect{x}_j]$ is an unknown coefficient sequence defined on
the point set $\pointset{T}_h$ that is to be determined from the
samples of $f$. The function
$\varphi_p$ is a periodized version of a generating function $\varphi$
and is defined as
\begin{equation}
\varphi_p(\vect{x}) := \sum_{\vect{m} \in \ints^s} 
\varphi\bigl(\vect{x} - \frac{2}{h} \vect{m} \bigr).
\label{eq:periodization}
\end{equation}

@@

It is easy to verify that, with this definition of $\varphi_p$,
$\appf{V}$ is also $\cube^s$-periodic. Even though we are only
interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending
$\appf{V}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz}
allows us to use the Fourier domain error kernel proposed by Jacob
\textit{et. al}~\cite{jacob02} to quantify the approximation error
$\LLnorm{V - \appf{V}}$.

Another simplification is in order here. Since the solution $V$ to the Poisson
problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look
for an approximate solution $\appf{V} \in \aspace{\lattice{L}_h}{\varphi_p}$
that is also odd in each variable. This can be achieved by setting
the boundary coefficients to zero and by requiring that the resulting sequence
be odd.  With $c[\vect{x}_j] = 0$ for $\vect{x}_j
\in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
\begin{equation}
\appf{V}(\vect{x}) = \sum_{j=1}^{2^sN} c[\vect{x}_j] 
\varphi_p(\frac{\vect{x} - \vect{x}_j}{h}).
\label{eq:simplifiedAnsatz}
\end{equation}
If the generator $\varphi$ is even and the sequence $c[\cdot]$ is odd,
the resulting approximation $\appf{V}$ is odd and satifies zero
Dirichlet boundary conditions (see Appendix~\ref{app:1}). With this
simplification, the coefficient sequence $c[\vect{x}_j]$ only needs to
be determined for $j \in \{1,\ldots,N\}$. The rest can be inferred
from oddity.

>>>>

Using the analytic solution~\eqref{eq:analytic} and the sine series
representation of the Green's function~\eqref{eq:green}, it is easy to show that
the solution is given by
\begin{equation}
  \st{\chi}[\vect{m}] = -
  \frac{\st{f}[\vect{m}]}{\pi^2 \norm{\vect{m}}^2},
\label{eq:fourierSolution}
\end{equation}
where $\vect{m} \in \ints^s_+$ and $\st{f}[\cdot]$ represents the Fourier
sine series coefficients of the odd extension of $f$. To facilitate subsequent
discussions, let us introduce the solution operator
$\stpairs{\invlaplacian}{\frac{1}{-\pi^2 \norm{\vect{m}}^2}}$  ($\vect{m} \in
\ints^s_+$), where the symbol $\stpairs{}{}$ represents how the Fourier sine
series coefficients are affected by the operator.
%\begin{equation}
%V(\vect{x}) = \invlaplacian\Bigl( f(\vect{x}) +
%\sum_{i=1}^s D^0_i g^0_i(\vect{x}) + D^1_i g^1_i(\vect{x}) \bigr), 
%\label{eq:operatorAnalytic}
%\end{equation}
The self-adjoint operator $\invlaplacian$ is the inverse of the Laplace
operator. Self-adjointness can be easily verified with
the aid of Parseval's relation, which states that
$
  \innerproduct{a}{b} = \sum_{\vect{m} \in \ints^s_+} \st{a}[\vect{m}]
  \st{b}[\vect{m}] 
$
for any $\cube^s$-periodic functions $a$ and $b$ that are in
$L_2(\cube^s)$ and odd.

@@

We wish to use the samples of $f$ to approximate the function $V$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
$\chi$ is a periodic function, we follow the recipe of Jacob \textit{et al.}~\cite{jacob02} and seek an approximation that lies in a space generated by a periodic reconstruction function. Specifically, we are interested in the case
where $\appf{\chi}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} := \mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and translated versions of a periodic function $\varphi_p$. Our approximation is given by
\begin{equation}
  \appf{\chi}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{T}_h} c[\vect{x}_j] 
\varphi_p\bigl(\frac{\vect{x} - \vect{x}_j}{h}\bigr),
\label{eq:ansatz}
\end{equation}
where $c[\vect{x}_j]$ is an unknown coefficient sequence defined on the point set $\pointset{T}_h$ that is to be determined from the samples of $f$. The function $\varphi_p$ is a periodized version of a generating function $\varphi$ and is defined as
\begin{equation}
\varphi_p(\vect{x}) := \sum_{\vect{m} \in \ints^s} 
\varphi\bigl(\vect{x} - \frac{2}{h} \vect{m} \bigr).
\label{eq:periodization}
\end{equation}

@@

It is easy to verify that, with this definition of $\varphi_p$,
$\appf{\chi}$ is also $\cube^s$-periodic. Even though we are only
interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending $\appf{\chi}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz} allows us to use the Fourier domain error kernel proposed by Jacob \textit{et. al}~\cite{jacob02} to quantify the approximation error $\LLnorm{\chi - \appf{\chi}}$.

Another simplification is in order here. Since the solution $\chi$ to the Poisson problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look for an approximate solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$
that is also odd in each variable. This can be achieved by setting
the boundary coefficients to zero and by requiring that the resulting sequence be odd.  With $c[\vect{x}_j] = 0$ for $\vect{x}_j \in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
\begin{equation}
\appf{V}(\vect{x}) = \sum_{j=1}^{2^sN} c[\vect{x}_j] 
\varphi_p(\frac{\vect{x} - \vect{x}_j}{h}).
\label{eq:simplifiedAnsatz}
\end{equation}
If the generator $\varphi$ is even and the sequence $c[\cdot]$ is odd,
the resulting approximation $\appf{V}$ is odd and satifies zero
Dirichlet boundary conditions (see Appendix~\ref{app:1}). With this
simplification, the coefficient sequence $c[\vect{x}_j]$ only needs to
be determined for $j \in \{1,\ldots,N\}$. The rest can be inferred
from oddity.
